Vagueness games

### 2014-08-27 data_exploration_round_based.Rmd
data exploration round based

data = read.csv('results/20140827-121341.round_based.csv')

ds = data[,c(1,4,7:12)] # only relevant data
dm = melt(ds,id.vars = c("Number.of.states", "Impairment", "Iterations")) # melted data

>>>>

data = read.csv('results/20140827-124230.round_based.csv')

ds = data[,c(1,4,7:8)] # only relevant data
dm = melt(ds,id.vars = c("Number.of.states", "Impairment", "Iterations")) # melted data
